---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# sloop

[![CRAN status](https://www.r-pkg.org/badges/version/sloop)](https://cran.r-project.org/package=sloop)
[![Travis build status](https://travis-ci.org/r-lib/sloop.svg?branch=master)](https://travis-ci.org/r-lib/sloop)
[![Codecov test coverage](https://codecov.io/gh/r-lib/sloop/branch/master/graph/badge.svg)](https://codecov.io/github/r-lib/sloop?branch=master)

The goal of sloop is to provide tools to help interactive explore and understand object oriented programming in R. For help creating new classes of S3 vector, see the [vctrs](https://vctrs.r-lib.org) package.

## Installation

You can install sloop from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("r-lib/sloop")
```

## Usage

```{r}
library(sloop)
```

sloop provides a variety of tools for understanding how S3 works. The most useful is probably `s3_dispatch()`. Given a function call, it shows the set of methods that are considered, found, and actually called:

```{r}
s3_dispatch(print(Sys.time()))
```

To the best of my ability it covers all the details of S3 including group generics, internal generics, implicit classes, and use of `NextMethod()`:

```{r}
# Implicit class
x <- matrix(1:6, nrow = 2)
s3_dispatch(print(x))

# Internal generic 
s3_dispatch(length(x))
s3_dispatch(length(mtcars))

# NextMethod
s3_dispatch(Sys.Date()[1])

# group generic
s3_dispatch(sum(Sys.Date()))
```

It also provides tools for determing what type of function or object you're dealing with:

```{r}
ftype(t)
ftype(t.test)
ftype(t.data.frame)

otype(1:10)
otype(mtcars)
otype(R6::R6Class()$new())
```

And for retrieving the methods associated with a generic or class:

```{r}
s3_methods_class("factor")

s3_methods_generic("summary")
```

